--- 
title: "Pathway enrichment analysis and visualization of omics data using g:Profiler, GSEA, Cytoscape and EnrichmentMap"
subtitle: "Updated to latest software versions"
author: "Ruth Isserlin"
date: "last modified `r Sys.Date()`"
site: bookdown::bookdown_site
output:   bookdown::gitbook
documentclass: book
bibliography: [references.bib]
biblio-style: nature.csl
link-citations: true
github-repo: baderlab/EnrichmentMap_Protocol
description: "updated version of nature protocol"
download: ["epub"]
---

# About

Original content was published [Reimand, J., Isserlin, R., Voisin, V. et al. Pathway enrichment analysis and visualization of omics data using g:Profiler, GSEA, Cytoscape and EnrichmentMap. Nat Protoc 14, 482–517 (2019). https://doi.org/10.1038/s41596-018-0103-9](https://www.nature.com/articles/s41596-018-0103-9) and this book only updates relevant steps in the protocol procedures section to reflect later versions of software packages. 
 
## Attributions:

This book was created using The **bookdown** package and can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

```{r include=FALSE}
#initialize the task counter
task_counter <- 0
```


Icons are from the [“Very Basic. Android L Lollipop” set by Ivan Boyko](https://www.iconfinder.com/iconsets/very-basic-android-l-lollipop) licensed under [CC BY 3.0](https://creativecommons.org/licenses/by/3.0/). 
